\textbf{Preprinting Microbiology}

### 2017-04-17 submission/Schloss_PrePrints_mBio_2017.tex

I am grateful to Stefano Bertuzzi and Lynn Enquist for their helpful
comments on earlier versions of this manuscript and to the numerous
individuals who provided feedback on the preprint version of the
manuscript. This work was supported in part by funding from the National
Institutes of Health (P30DK034933). I appreciate the support of
Altmetric, Inc and Thompson Reuters who provided advanced programming
interface (API) access to their databases. The workflow utilized
commands in GNU make (v.3.81), GNU bash (v.4.1.2), and R (v.3.3.2).
Within R I utilized the cowplot (v.0.6.9990), dplyr (v.0.5.0), ggplot2
(v.2.1.0.9001), httr (v.1.2.1), RCurl (v.1.95-4.8), rentrez (v.1.0.4),
rjson (v.0.2.15), rvest (v.0.3.2), sportcolors (v.0.0.1), and tidyr
(v.0.6.0) packages. A reproducible version of this manuscript and
analysis is available at
\url{http://www.github.com/SchlossLab/Schloss_PrePrints_mBio_2017}.

>>>>

I am grateful to Stefano Bertuzzi and Lynn Enquist for their helpful
comments on earlier versions of this manuscript and to the numerous
individuals who provided feedback on the preprint version of the
manuscript. This work was supported in part by funding from the National
Institutes of Health (P30DK034933). I appreciate the support of
Altmetric, Inc and Thompson Reuters who provided advanced programming
interface (API) access to their databases. The workflow utilized
commands in GNU make (v.3.81), GNU bash (v.4.1.2), and R (v.3.3.2).
Within R I utilized the cowplot (v.0.6.9990), dplyr (v.0.5.0), ggplot2
(v.2.1.0.9001), httr (v.1.2.1), RCurl (v.1.95-4.8), rentrez (v.1.0.4),
RJSONIO (v.0.2.15), rvest (v.0.3.2), sportcolors (v.0.0.1), and tidyr
(v.0.6.0) packages. A reproducible version of this manuscript and
analysis is available at
\url{http://www.github.com/SchlossLab/Schloss_PrePrints_mBio_2017}.
